Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-03-20 paper/main.tex
polished third optimization

The third optimization adds to each formula $\Phi_{j,C,K}$ a conjunct
\[
   \bigwedge_{c\in\{1,2,\ldots,C\}}\bigwedge_{k\in N_K} \neg
   i_{c,k}~\vee~\neg f_{c,k}
\]
saying that any cube does not contain both $\Inf k$ and $\Fin k$ for any
$k$ as such a cube cannot be satisfied by any run.

@@

\begin{table}[t]
\caption{The effect of reduction.
A cell on coordinates $(x,y)$ contains the number of automata that have been
reduced from $x$ to $y$ acceptance marks. If the cell contains a sum of two
numbers, the latter represents number of automata where the last call to QBF
solver reached the time limit.}
\label{tab:heatmap}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap.tex}
\end{table}

@@

\begin{figure}[b!]
  \caption{Performance of \telatko on individual automata of each automata sets.
    The graph shows the time ($y$ axis) needed by \telatko
    to process the $x$-th automaton of the set, where automata of each set are ordered by their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}
\bigskip
\centering
\input{quantile.tex}
\end{figure}

>>>>

The third optimization extends $\Phi_{j,C,K}$ into the conjunction
\[
   \Phi_{j,C,K}~\wedge \bigwedge_{c\in\{1,2,\ldots,C\}}\bigwedge_{k\in N_K} (\neg
   i_{c,k}\vee\neg f_{c,k}).
\]
The added part says that any cube does not contain both $\Inf k$ and
$\Fin k$ for any $k$. A cube with both $\Inf k$ and $\Fin k$ would be
useless as it cannot be satisfied by any run.

@@

\begin{table}[b!]
\caption{The effect of reduction.
A cell on coordinates $(x,y)$ contains the number of automata that have been
reduced from $x$ to $y$ acceptance marks. If the cell contains a sum of two
numbers, the latter represents number of automata where the last call to QBF
solver reached the time limit.}
\label{tab:heatmap}
\setlength{\tabcolsep}{2.5pt}
\centering
\input{table-heatmap.tex}
\end{table}

@@

\begin{figure}[t]
  \caption{Performance of \telatko on individual automata of each automata sets.
    The graph shows the time ($y$ axis) needed by \telatko
    to process the $x$-th automaton of the set, where automata of each set are ordered by their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}
\bigskip
\centering
\input{quantile.tex}
\end{figure}
